Numerical experiment investigating the influence of drag on trajectory patterns of floating macroalgae

### 2021-05-03 thesis_chapter_3.Rmd
final comments AJ. new output

To test the different magnitudes that hydrodynamic and wind drag might play in the overall trajectory, simulations were run with varying degrees of drag exposure scenarios. These scenarios were meant to act as proxy for buoyancy, which determines the surface area exposed to hydrodynamic and wind drag. These estimates were expressed as percentages which were used to calculate hydrodynamic and wind drag for applicable simulation. For example, if 85% of the plant is submerged and 15% of above water, then the overall hydrodynamic and wind drag forces would be 85% and 15% of the total drag forces respectively. This approach has been used in past research investigating pelagic *Sargassum* rafts [@putman2020;@putman2018]. The exposure scenarios used in this study were 100%, 95%, 90%, and 85% for hydrodynamic drag; 0 %, 5%, 10%, and 15% for wind (see table 1). Each scenario consisted of a particle set with a size of 1000 were released from Kommetjie at the start of simulation. Since the aim of this investigation was to investigate the relative surface behavior of virtual kelp particles, only the surface layer was used for simulations. It should also be noted that the Copernicus model (see below) used places velocity vectors over some of the land covering the coastal domain. This was not considered a concern, as once again, the aim was to investigate surface drift behavior. A summary of the parameters for each simulation are provided in table 1. To determine if vortices and eddys play a role in kelp accumulation on the surface, a separate set of simulations were performed. Unlike the previous simulations, these simulations released a particle every hour over the same time periods.

@@

sim_table <- flextable(data = sim_table)
sim_table <- theme_zebra(sim_table, odd_header = "transparent", even_header = "transparent")
sim_table <- set_header_labels(sim_table, Cross.sectional.area = "Cross-sectional area", Drag.Exposure = "Drag Exposure level")
sim_table <- align(x= sim_table, align = "center", part = "all")
sim_table <- set_table_properties(sim_table, width = 1, layout = "autofit")
sim_table <- set_caption(sim_table, "Details for each simulation run for the study. Type refers to either a passive particle with no drag behavior or a kelp particle that has been advected with any drag exposure. The drag exposure column refers to the parameterizations regarding the level of water and wind drag simulated. All simulations were run with a Runge-Kutte (4th) advection scheme, Brownian motion, 30 days, and included 1000 particles for a 2018 hindcast.")
sim_table

@@

area_table <- read.csv("tables/chapter_3/area_table.csv", sep = ";")
area_table <- flextable(data = area_table)
area_table <- theme_zebra(area_table, odd_header = "transparent", even_header = "transparent")
area_table <- align(x= area_table, align = "center", part = "all")
area_table <- set_header_labels(area_table, Plant.characteristic = "Plant characteristic", Approximate.shape = "Approximate shape", Equation.used = "Equation Used", Plant.dimensions = "Plant dimensions")
area_table <- set_header_labels(area_table, Ac.Minimum = "Ac Minimum", Ac.Mean = "Ac Mean", Ac.Maximum = "Ac Maximum")
area_table <- set_table_properties(area_table, width = 1, layout = "autofit")
area_table <- set_caption(area_table, "Table 2: Table summarising the attributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulations. Approximate shape refers to the dimensions of the geometric shape used to represent a particular morphological characteristic. Equations used are the equations relating to the dimensions used for the geometric shape estimate. Plant dimensions are the measurements used, collected in previous work by @coppin2020, used to calculate the associated surface areas. The total surface areas for each plant characteristic for each surface area type make up the remaining columns.")
area_table
```
## Analysis

@@

waterdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water_April, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill ="grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww_April, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water_July, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww_July, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_Oct <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water_Oct, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_Oct <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww_Oct, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  guides(fill=guide_legend(title="Number of particles")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

heatmap_RK4_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

heatmap_RK4_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean_April, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean_April,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc_April, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc_April, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

heatmap_RK4_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc_July, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc_July, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

>>>>

To test the different magnitudes that hydrodynamic and wind drag might play in the overall trajectory, simulations were run with varying degrees of drag exposure scenarios. These scenarios were meant to act as proxy for buoyancy, which determines the surface area exposed to hydrodynamic and wind drag. These estimates were expressed as percentages which were used to calculate hydrodynamic and wind drag for applicable simulation. For example, if 85% of the plant is submerged and 15% of above water, then the overall hydrodynamic and wind drag forces would be 85% and 15% of the total drag forces respectively. This approach has been used in past research investigating pelagic *Sargassum* rafts [@putman2020;@putman2018]. The exposure scenarios used in this study were 100%, 95%, 90%, and 85% for hydrodynamic drag; 0 %, 5%, 10%, and 15% for wind (see table 1, Appendix). Each scenario consisted of a particle set with a size of 1000 were released from Kommetjie at the start of simulation. Since the aim of this investigation was to investigate the relative surface behavior of virtual kelp particles, only the surface layer was used for simulations. It should also be noted that the Copernicus model (see below) used places velocity vectors over some of the land covering the coastal domain. This was not considered a concern, as once again, the aim was to investigate surface drift behavior. A summary of the parameters for each simulation are provided in table 1. To determine if vortices and eddys play a role in kelp accumulation on the surface, a separate set of simulations were performed. Unlike the previous simulations, these simulations released a particle every hour over the same time periods.

@@

@@

area_table <- read.csv("tables/chapter_3/area_table.csv", sep = ";")
area_table <- flextable(data = area_table)
area_table <- theme_zebra(area_table, odd_header = "transparent", even_header = "transparent")
area_table <- align(x= area_table, align = "center", part = "all")
area_table <- set_header_labels(area_table, Plant.characteristic = "Plant characteristic", Approximate.shape = "Approximate shape", Equation.used = "Equation Used", Plant.dimensions = "Plant dimensions")
area_table <- set_header_labels(area_table, Ac.Minimum = "Ac Minimum", Ac.Mean = "Ac Mean", Ac.Maximum = "Ac Maximum")
area_table <- set_table_properties(area_table, width = 1, layout = "autofit")
area_table <- fontsize(area_table, size = 8, part = "body")
area_table <- fontsize(area_table, size = 8, part = "header")
area_table <- set_caption(area_table, "Table 2: Table summarising the attributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulations. Approximate shape refers to the dimensions of the geometric shape used to represent a particular morphological characteristic. Equations used are the equations relating to the dimensions used for the geometric shape estimate. Plant dimensions are the measurements used, collected in previous work by @coppin2020, used to calculate the associated surface areas. The total surface areas for each plant characteristic for each surface area type make up the remaining columns.")
area_table
```
## Analysis

@@

waterdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water_April, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_April <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill ="grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww_April, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water_July, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") + 
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_July <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww_July, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

waterdrag_plot_Oct <- ggplot()+
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_water_Oct, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw()

wwdrag_plot_Oct <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0,     colour = "black",     fill = "grey") +
  coord_cartesian(xlim = c(8, 28), ylim = c(-38, -26)) +
  geom_path(data = total_mean_ww_Oct, aes(x = lon, y = lat, colour = type))+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  scale_colour_discrete("Type") +  
  guides(fill=guide_legend(title="Number of particles")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw()

@@

heatmap_RK4_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

heatmap_RK4_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean_April, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean_April,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc_April, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc_April, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

heatmap_RK4_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = pass_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Passive particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_kelp_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_path(data = kelp_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("Kelp particles") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_RK4_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = pass_acc_July, aes(x = lon, y = lat, colour = distance)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

point_kelp_acc_July <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_point(data = kelp_acc_July, aes(x = lon, y = lat, colour = age)) +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) +
  xlab("Longtitude") +
  ylab("Latitude") +
  ggtitle("") +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
